%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Explanation of the Work carried out
%%% by the Beneficiaries and Overview of 
%%% the Progress
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage
\section{Explanation of the Work carried out by the Beneficiaries and Overview of the Progress}
\label{sec:work-carried-out}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Section content, please change!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%\textcolor{blue}{Text provided by Navin - EUROpean Laboratories for Accelerator Based Sciences (EURO-LABS) is a pioneering project in Europe to build the foundations for creating synergies and collaborations between the Research Infrastructures (RI) of the Nuclear and High Energy communities. This is the first time such and “experiment” of combing three big communities of Europe engaged in Nuclear Physics and accelerator/detector technology for High Energy Physics, involved in curiosity-driven research and its technical and societal offshoots. EURO-LABS endeavor to this fusion is going from strength to strength in achieving the goals we have defined and improving the amalgation of this subatomic community of Europe. The EURO-LABS community is not exploiting ESFRI facilities and  CERN but also  relatively smaller facilities but  very successfully  using their complementarity  more than 2 years  and is demonstrating unity in diversity. will enhance Europe’s potential for successfully facing the upcoming new challenges. The key objective of EURO-LABS of  promoting and facilitating access to improved available resources (thorugh service imporvements)  at a major fraction of EUROpean Laboratories for Accelerator Based Science with an emphasis on young students or early-career is running smoothly and successfully.} 
EURO-LABS (European Laboratories for Accelerator Based Sciences) is a pioneering initiative in Europe aimed at fostering synergies and collaboration among the Research Infrastructures (RIs) of the nuclear and high-energy physics communities. For the first time, this ambitious "experiment" brings together three major European communities involved in nuclear physics and accelerator/detector technologies for high-energy physics — each engaged in curiosity-driven research and its technological and societal applications.

EURO-LABS is steadily progressing in its mission, strengthening the integration of Europe’s subatomic science community. The project is making effective use of a wide range of facilities — not only large-scale ESFRI infrastructures and CERN, but also smaller laboratories. By leveraging their complementarity, the community has successfully demonstrated "unity in diversity" for over two years.

This collaborative approach significantly enhances Europe’s capacity to tackle future scientific and technological challenges. A key objective of EURO-LABS is to promote and facilitate access to upgraded resources (through service improvements) across a large portion of European laboratories specializing in accelerator-based science. Special emphasis is placed on supporting young researchers and early-career scientists, and this effort is progressing successfully.

This section summarizes the work carried out by the \acrshort{euro-labs} consortium during the \nth{2} \acrshort{RP} towards the project goals and work plan as described in the \acrfull{GA} (see Annex 1 - Description of the action (part B), art. 3.1 Work plan and resources).
%\cite{bib:grantagreement2020}.

\subsection{Objectives}

The main goals of the project as described in section 1.1 of the Declaration of Actions (DoA) are listed below: 
\begin{tcolorbox}[myliststyle]
\begin{enumerate}[label=\textbf{\arabic*.}, nosep, left=0pt]
    \item Setup simplified and more efficient access procedures to an enlarged and diverse portfolio of leading RIs and installations located across Europe, to offer dedicated beam-time attributed to EURO-LABS, at no cost to the users, primarily for conducting research in Nuclear and High-Energy Physics. These RIs, potentially also attractive to related disciplines are expected to fertilize synergies and activities related to applications via a wider sharing of information, knowledge and technologies across scientific fields.
    \item Organize and facilitate the effective use of the RIs by providing expert help to visiting teams, to optimally plan and exploit the full capabilities of the facilities for cutting-edge research. Create reference documentation and publicise the specifications and features of each RI along with examples of some key experiments or tests that can be conducted. This will allow research teams to choose the best RI (RIs) for their investigations
    \item Additionally conduct collaborative targeted improvements for the existing services that will lead to an increase of the scientific and technical opportunities at various RIs.
    \item Make the results from the tests conducted at the RIs of EURO-LABS during the period of the project freely available to the scientific community and manage the experimental data, when relevant, through a Data Management Plan (DMP) in line with the FAIR principles (Findable, Accessible, Interoperable, Reusable).
    \item Organize the training of the new generation of researchers and young technical staff to best exploit the RIs, through workshops and hands-on experience at specifically chosen RIs.
\end{enumerate}
\end{tcolorbox}

%In pursuit of these overarching goals, specific objectives have been defined for each WP for P1. A summary of the progress towards these objectives is provided below.

%\textcolor{blue}{Text provided by Navin - Below the   work done in this reporting period  P2 for the five Work Package (WP)s are described. The first one deals with project management and coordination. Three work packages deal with the utilization of a variety of accelerators and associated technological centres having a very wide range of characteristics, from Nuclear Physics (and a virtual computing facility for planning and interpreting experimental data) infrastructures to RIs for Accelerator and Detector R\&D. The last WP deals with Open Diverse and Inclusive Science, including development of machine learning techniques, promotion of FAIR principles and training. The project activities funded by EURO-LABS in this reporting period like the last one cover cover a broad range of science and technology exploiting the complementarity of the facilities. Some highlights include for e.g  tests of "the first 2 meters FCC" components FCC-hh beam screen \& FCC-ee vacuum chamber prototypes tested in CERN's BESTEX beam-line at KARA. The Electro Magnetic Compatibility centre at greatly  increased throughput  (service improvements) as the result of collaboration in two projects  EURO-LABS  and  AIDAINNOVA. Complementary R and D for FLASH Therapy in the  WP2 GSI-FAIR  Synchrotron WP3 CLEAR CERN  LINAC WP4 IFJ PAN  Cyclotron. A irradiation campaign at TRIGA (service improvements) DRD3  for  ESPP to study fluences up to 1016 neq/cm2 (1018 neq/cm2) for HL-LHC (FC-HH). One example of  optimizing the  transnational access in EURO-LABS in WP2 was the work done by an  Italian led team  exploiting the complementary expertise and equipments in Krakow (IFJ PAN) and Bucharest(IFIN). The goal was to  measure  the temperature and isospin dependence oscillations of the neutron skin  to obtain  the equation of state in neutron star mergers,  to understand the isotope abundance the universe.  Below are a details of   work done during this Reporting Period(P2).}
In pursuit of these overarching goals,
during this reporting period (P2), significant progress was achieved across the five Work Packages (WPs) of the EURO-LABS project.

\begin{description}
    \item[WP1] focused on project management and coordination, ensuring effective collaboration and oversight across all activities.
    
    \item[WPs 2 to 4] were dedicated to the utilization of a diverse range of accelerator facilities and associated technological centers. These cover a wide spectrum of infrastructures, from nuclear physics facilities --- including a virtual computing facility for experimental planning and data analysis --- to research infrastructures (RIs) for accelerator and detector R\&D.
    
    \item[WP5] addressed Open, Diverse, and Inclusive Science. Key activities included the development of machine learning techniques, promotion of FAIR (Findable, Accessible, Interoperable, and Reusable) data principles, and the organization of training initiatives.
\end{description}

The activities funded by EURO-LABS during this period, like in the previous one, spanned a wide range of scientific and technological domains, leveraging the complementary capabilities of participating facilities. A few highlights are mentioned below: 



\begin{itemize}
    \item {\it Accelerator and Component Testing:} The FCC-hh beam screen and FCC-ee vacuum chamber prototypes (the ``first 2 meters FCC'' components) were tested in CERN's BESTEX beamline at KARA.
    
    \item {\it Service Improvement:} The Electro-Magnetic Compatibility Center achieved significant improvements in throughput and services, thanks to collaborations within EURO-LABS and AIDAINNOVA. Moreover, at the TRIGA reactor, a campaign under DRD3 for ESPP  was conducted to study fluences up to \(10^{16} \, \text{neq/cm}^2\) and \(10^{18} \, \text{neq/cm}^2\), supporting experiments for HL-LHC and FCC-hh.
    
    \item {\it FLASH Therapy R\&D:} Complementary research activities for FLASH therapy were carried out using
%\begin{itemize} \item 
        the GSI-FAIR synchrotron (WP2),
        the CLEAR facility at CERN LINAC (WP3)
        and the IFJ PAN Cyclotron (WP4).
 %   \end{itemize}
    
    \item {\it Transnational Access Optimization:} An Italian-led team leveraged the complementary expertise and equipment of IFJ PAN (Krakow) and IFIN (Bucharest) to study temperature and isospin dependence of neutron skin oscillations. The goal was to inform the equation of state for neutron star mergers and advance understanding of isotope abundances in the universe.
\end{itemize}



This report illustrates the breadth and depth of scientific and technological achievements supported by EURO-LABS in Reporting Period P2. The collaborative efforts across work packages and Research Infrastructures continue to produce impactful outcomes across a wide range of disciplines.


\tsubsubsection{WP1 - Management}

% \sout{%
% \begin{minipage}{\textwidth}
%The administrative management of the EURO-LABS is carried out by the Project office (PO) The management of the project is done along with the Management team (MT) and the Steering Committee (SC). It report to the Governing board and the laisses with EU Project officer.
%The specific objectives include:
%\begin{itemize}
%    \item financial follow-up include of resource utilisation, cost reporting and collection, reviews,
%    \item submission of the Financial Statements of all beneficiaries, as well as the distribution and payments of the EU funding,
%    \item monitor, review and release of the Deliverables and Milestones reports,
%    \item provide periodically relevant information to the beneficiaries,
%    \item implement strategic issues, such as modifications of the project programme of work, and admission of new beneficiaries as decided by the GB,
%    \item announce and provide the relevant instruction of all the possibilities   proposed by the various research infrastructures of EURO-LAB for transnational access and job opening available in the project.
%\end{itemize}
% \end{minipage}
% }

%\textcolor{blue}{The Project office (PO) is responsible for all administrative processes of  EURO-LABS and is coordinated  by INFN. Along with the PO, the management team (MT) and the Steering Committee (SC) coordinate and ensure the smooth and timely running of the project and  report to the Governing Board (GB). The PO liaises with the EU Project officer.The specific objectives include: 
%- financial follow-up including resource utilisation, cost collection and reporting, reviews, 
%- submission of the Financial Statements of all beneficiaries, as well as the distribution and payments of the EU funding, 
%- monitor, review and release of the Deliverables and Milestones reports, 
%- provide periodically relevant information to the beneficiaries, 
%- implement strategic issues
%- announce and provide the relevant instruction of all the possibilities at  the various research infrastructures of EURO-LAB for transnational access
%- providing   contacts and daily helpdesk via email, telephone and remote meetings.
%All the Deliverables and Milestones have been monitored and completed in P2. These Reports are available on the F\&T portal and, when public, also through the Zenodo repository and linked to the project website.
%Regular bi-meetings of the Steering Committee/ Management Team were held Also periodic management meetings of the Project Office staff were held, involving people from INFN Bologna, INFN Frascati and CERN. Two in -person annual meetings were held in the period. These meeting are very important as it further strengthens the ties and appreciation of the various activities.  
%SAM (Second Annual Meeting) was organized by IFJ-PAN was  held in Krakow, Poland (9th-11th October 2023. It was attended by 83 participants. Details of the diverse program are available https://agenda.infn.it/event/34651/)
%TAM (Third Annual Meeting) was organized by and held at CERN, Geneva, Switzerland (28th-30th October 2024. It was attended by 85 participants.
%During the annual meetings, well appreciated guided tours were also organized to IFJ-PAN and CERN facilities also so the various communities are aware of the various strengths of EURO-LABS.  A well planned  agenda allowed the three scientific communities to  shared their experiences on TNAs and also show case various activities. Complementary nature of the various EURO-LABS infrastructure is highlighted. TAM took a new format with a large  focus on the presentation of selected scientific and technical presentation of work done at facilities in the form of  oral and poster presentations. A few talks connected to the long-term plans of the three communities of EURO-LABS for the coming decades related to the European Stradegy for Particle Physics and the NuPECC long range plan for Nuclear Physics There was also a dedicated talk about the  FCC. The presentations as available https://indico.cern.ch/event/1370378/)
%A Governing Board meetings were held during each of the annual meetings (respectively, 11th Oct. 2023 and 29th Oct. 2024.) They were actively attended with only a very few participants attending on zoom. During the 2024 GB meeting, the Chairperson's mandate was renewed for another two years. Various procedures to facilitate reallocation or balancing of resources for trans-national access were finalized. The decisions for the transfer of funds for optimum usage of Transnational access  will discussed in the next GB meeting. It will be held during the Fourth Annual Meeting of EURO-LABS  (FAME) will be held at  will be held at the Jozef Stefan Institute, Liubljana, 29th Sept.-1st Oct. 2025 }

The Project Office (PO), coordinated by INFN, is responsible for managing all administrative processes of EURO-LABS. Together with the Management Team (MT) and the Steering Committee (SC), the PO ensures the smooth and timely execution of the project and reports to the Governing Board (GB). The PO also serves as the liaison with the EU Project Officer.

The specific responsibilities of the PO are:

\begin{itemize}
    \item Financial oversight, including resource utilization, cost tracking and reporting, reviews
    \item Submission of Financial Statements on behalf of all beneficiaries, as well as the distribution and payment of EU funding
    \item Monitoring, reviewing, and releasing Deliverables and Milestones reports
    \item Providing beneficiaries with regular updates and relevant information
    \item Implementing strategic decisions, such as modifications of the project program of work, and admission of new beneficiaries as decided by the GB
    \item Announcing and providing guidance on transnational access opportunities at EURO-LABS research infrastructures
    \item Offering daily helpdesk support via email, phone, and remote meetings
\end{itemize}

All Deliverables and Milestones were monitored and successfully completed in P2. These reports are available on the Funding \& Tenders Portal and, when public, on the Zenodo repository and linked to the project website.


Regular bimonthly meetings of the Steering Committee and Management Team were held, as well as periodic management meetings involving Project Office staff from INFN Bologna, INFN Frascati, and CERN. Additionally, two in-person annual meetings were conducted during this period, playing a crucial role in strengthening collaboration and mutual appreciation of the project activities. Organized by IFJ-PAN, SAM (Second Annual Meeting) was held in Krakow, Poland from 9th to 11th October 2023 and was attended by 83 participants. Details of the program are available at:
%\begin{center}
    \url{https://agenda.infn.it/event/34651/}.
%\end{center}
TAM (Third Annual Meeting) was organized by and hosted at CERN in Geneva, Switzerland from 28th to 30th October 2024 and welcomed 85 participants. The annual meetings included guided tours of IFJ-PAN and CERN facilities, showcasing the strengths of EURO-LABS' diverse research infrastructures. A well-structured agenda facilitated the exchange of experiences among the three scientific communities, particularly in relation to Transnational Access (TNA) activities. TAM introduced a new format with a strong focus on scientific and technical presentations, featuring oral and poster sessions. Several talks also addressed long-term plans of the EURO-LABS communities in connection with the European Strategy for Particle Physics and the NuPECC Long Range Plan for Nuclear Physics. A dedicated talk on the Future Circular Collider (FCC) was also included. Presentations are available at:
%\begin{center}
\url{https://indico.cern.ch/event/1370378/}.
%\end{center}

Governing Board (GB) meetings were held during each of the annual meetings (11th October 2023 and 29th October 2024). These meetings were well attended in person, with minimal virtual participation. During the 2024 GB meeting, the Chairperson’s mandate was renewed for another two years.

Procedures for reallocating or balancing resources to optimize Transnational Access were finalized. The decisions regarding fund transfers will be discussed at the next GB meeting, that will take place during the Fourth Annual Meeting of EURO-LABS (FAME).  FAME will be held at the Jožef Stefan Institute in Ljubljana, from 29th September to 1st October 2025.



\tsubsubsection{WP2 - Access to RI for Physics}

WP2 provides Transnational Access (TA) to fourteen (14) RIs for fundamental and applied nuclear physics experiments and to two (2) facilities providing TA and Virtual Access (VA) for related theoretical support. 
The specific objectives for P2 included: 
\begin{itemize}
    \item continuation of the provision of TA at European accelerator facilities offering a stable or radioactive ion or neutron beams,
    \item create and use of synergies between theory and experiments through TA offered at the ECT* (European Centre for Theoretical Studies in Nuclear Physics and Related Areas (ECT*) and VA through the newly founded Theo4Exp facility,
    \item improve further the services offered to users at several RIs.
\end{itemize}

In this RP, progress has been made on all the objectives indicated above.
In particular, a progress towards complementary use of different installations is evidenced. 
One example of  optimizing the  transnational access in EURO-LABS in WP2 was the work done by an  Italian led team  exploiting the complementary expertise and equipments in Krakow (IFJ PAN) and Bucharest(IFIN). The goal was to  measure  the temperature and isospin dependence of the oscillations of the neutron skin  to obtain also information on the equation of state in neutron star mergers and to understand the isotope abundance the universe. 
 
\tsubsubsection{WP3 - Access to RI for Accelerators}

WP3 is connected to the provision of TA to RIs related primarily to High Energy Accelerator R\&D. The WP groups fourteen (14) facilities located in eleven (11) research laboratories, spread out across Europe. The facilities are grouped into four Tasks, targeted to specific areas of R\&D: material testing, technology infrastructures, electron and laser beams, and applications. 

During this reference period, the focus was on delivering transnational access to all facilities as described in the MS17 report, while in parallel progressing with the service improvements outlined in the MS19 report. 
Significant and tangible progress was made toward both objectives across the majority of the facilities. As described in MS17, not all WP3 facilities were expected to be fully operational in P1 due to ongoing technical work or upgrades. Some facilities were able to compensate for their delayed startup by delivering more Access Units (AU) than the fractional amount corresponding to the 18 months of P2.
Unfortunately, unexpected technical or administrative issues during the reference period continued to block four facilities from delivering transnational access, and a safety incident further delayed the startup of a fifth facility. Nevertheless, 78\% of the total possible AU for the P2 period were delivered, achieving a cumulative 58\% delivery from the start of the project.

The User Selection Panels (USP) per Task established in P1, involving external experts at 50\% level,  continued with only a recent change, and operated successfully throughout the reference period as required. 

Regarding the service improvements, good progress was made during the reference period, with implementation gradually starting — and in some cases, already well advanced.

% Highlights of the completed projects in the WP3 facilities during P2 are described in the following sections of this report.

\tsubsubsection{WP4 - Access to RI for Detectors}

WP4 serves to provide TA to top level European RIs for R\&D on detectors. Transnational access to RIs is well tailored, in terms of freely available resources at facilities, to the needs of detector R\&D where dedicated funding is often a problem. The slate of RIs is chosen to match the needs of European (and wider) detector R\&D carried out in the framework of DRD collaborations, set up by ECFA, and monitored by DRDC. The access is spread over three (3) types of research infrastructures, grouped into tasks: test beams (3 facilities), detector characterization (2 facilities), and irradiations (6 facilities). Service Improvements (Task 4) are planned at each RI to improve user access.

The key objective of WP4 in P2 was to continue running the TA framework for executing user projects of high relevance to the detector R\&D community. The overall success was excellent, but not entirely uniform across the RIs. The 105 additional projects, executed in P2, brought the total user count in P1\&P2 to more than 500 users and consumed already 94\% of the total access unit allocation. The USP common to all WP4 RIs is well in place; TA project applications are accepted with a high success rate due to careful pre-evaluation by the Facility Coordinators. With the commitment of the RIs, which spent most of their access allocation in P1\&P2, to provide additional resources, the RIs of WP4 will be continuing to facilitate Detector R\&D during the entire four years of the EURO-LABS project. Consorted measures have been taken to bring the few under-performing RIs to their expected performance in the remaining duration of the project.



\tsubsubsection{WP5 - Open Diverse and Inclusive Science}


 WP5 
 %assumes the transversal activities of the EURO-LABS project, 
 %starting by publicizing the project using traditional and modern means, enhance diversity in the different communities, bring nuclear physics into the EOSC framework, develop services to enhance FAIR data principles, promote the use of machine learning methods  to improve beam quality, transport efficiency and accelerator reproducibility and train young generations to make the European facilities better performing and more competitive: 
 is responsible for the transversal activities of the EURO-LABS project. These activities include promoting the project through both traditional and modern communication channels, fostering diversity across the involved scientific communities, and integrating nuclear physics into the European Open Science Cloud (EOSC) framework. WP5 also focuses on developing services to enhance FAIR data principles, promoting the use of machine learning techniques to enhance beam quality and transport efficiency, and accelerator reproducibility. In addition, WP5 aims to train the next generation of researchers, thereby improving the performance and competitiveness of European research facilities.
 The specific objectives for P2 are: 
\begin{itemize}
    \item continue fostering and monitoring the user diversity by engaging people of different nationalities, gender, age and level of expertise,
    \item enhance communication on project opportunities and dissemination of the project results, also through the use of social media platforms,
    \item continue to promote the development of FAIR (Findable, Accessible, Interoperable Reusable) research data management practices within the scientific community,
    \item deploy a  new developed tool, based on machine learning techniques, for accelerator control, at (at least) two facilities,
    \item organize training activities, as planned in the DoA for RP2.
\end{itemize}
In this second reporting period, large progress has been made on all the objectives indicated above. In order to advertise EURO-LABS and disseminate its activities, the website has been continuously improved, to make the information more easily accessible to the users.  
The videos of the  39 facilities were completed. 
%It is consider that the videos are very important for advertising all facilities and particularly for the small ones that have no means to accomplish this good presentation card. 
As promised, we also initiated a Newsletter to advertise results and announce new initiatives, meetings and schools. The Newsletters were distributed well beyond the EURO-LABS lists, using all distribution lists existing in the community. Following the recommendations, EURO-LABS activities on social media platforms have started.
The authentication and authorization service for the community, provided within Task 5.2, is now being used for the Virtual Access activities of WP2. Concerning open data, a prototype of the OpenNP catalog 
has been developed and prepared for the deployment. The new GeOFF(Generic Optimization Framework
and Front-End) toolkit was deployed at GSI and CERN and used for beam optimization. The preparations to use GeOFF at CEA are ongoing.
Two Basic Training Schools (BTS) and two Advanced Training Schools, one on Operation
of Accelerators and the other dedicated to Open Data were organized.
Two schools were co-sponsored in 2024. Due to the high demand and as continuation of the planned program, an additional basic training school will take place in June in Seville and an advanced one on operation of accelerators will take place in May at CERN.

\tsubsubsection{WP6 - Ethic requirements}
%\textcolor{blue}{Text provided by Navin - In the Ethics Report 101057511\_EURO-LABS\_EthSR, only  two points were identified in connection with ethics requirements. These are   related to the health and safety during experiments and training activities and development of machine learning methods for beam delivery . The Ethics advisor, Prof. M. Harakeh presented his report in October 2025 to the project officer which mentioned that all activities of the consortium are in line with these ethics requirements and that  no new ethical issues have arisen since. More  details  of the two topics and the related steps taken are available as EURO-LABS Deliverable 6.1.
%The corresponding actions taken and that continue  be taken for these two points are briefly discussed here.
%\textbf{Health and safety during experiments and training activities: }
%EURO-LABS provides transnational access (TA) to a very large number of laboratories for Accelerator Based Sciences to users for conducting state-of-the-art research. Experiments in these laboratories involve working in areas  than could involve exposure to ionising radiation which could  result in harm to researchers, the public and the environment.  It is worth noting that EU-based facilities providing TA to users are subject to EU radiation protection legislation, in addition to their national legislations. Facilities outside the EU have equally strong rules for ensuring the high level of health and safety protection. The procedures put in place and adopted within EURO-LABS ensure that health and safety are guaranteed during experiments and training.  Specific safety training are organised periodically and is mandatory for all employees. Safety procedures are implemented for all accelerators and large installations. Radiation workers, in particular, undergo as well periodical training and tests. In addition to undergoing general safety training and radiation safety training, visitors must have health insurance. All users are equipped with personal dosimeters. During the schools organised by EURO-LABS for hands-on training at the facilities where the schools were organised the similar rules (in the case of work involving exposure to ionising radiation) were applied to visiting lecturers and students 
%\textbf{ The development of machine learning methods:} The project in Work package 5.3 also involves the use of Machine Learning (ML) methods to improve beam quality, transport efficiency and accelerator reproducibility in order to reduce the tuning time. It is necessary to ensure the transparency and robustness of the results in order to prevent biases and attention is being paid to the ethical risks related to the development and use of ML. These methods in principle could have a potential use in the medical sector, thus impacting patients. Such a use is not part of the present project. The developed/used ML methods is and will continue to be consistent with the ethical principles and requirements in accordance with the Ethics by design approach in all the design, acquisition, implementation and monitoring phases (cfr. Ethics By Design and Ethics of Use Approaches for Artificial Intelligence (EC documents 25 November 2021)).

%The goal of ML in this project deals with decreasing the amount of time spent on tuning of the beams that need to be provided to the Transnational Users of EURO-LABS, thus increasing and optimise the time available for research and technological studies and reduce power consumption. The use of ML is restricted to very limited choice of settings for machine parameters, such as devices necessary to optimise the optical properties of the beams delivered to the users and cannot modify any arbitrary machine parameter.  Any kind of bias in the algorithm could only possibly affect properties of the particle beam, e.g., its intensity, size and other similar properties and is easily and fully measurable through beam monitoring devices. the algorithms that are used so far are completely deterministic. The algorithms used are robust i.e., small changes of external circumstances do not cause failures in the algorithms. The application of ML in the project is robust, transparent and independent of bias for accelerator tuning for optimising the time available to the Transnational Users. The consortium continues to monitor and be compliant with its activities so as to keep the highest ethical standards.


In the Ethics Report \textbf{101057511\_EURO-LABS\_EthSR}, two ethics-related points were identified: (1) health and safety during experiments and training activities, and (2) the development of machine learning methods for beam delivery. The Ethics Advisor, Prof. M. Harakeh, presented his report to the Project Officer in October 2024, confirming that all consortium activities align with the relevant ethics requirements and that no new ethical issues have emerged. Additional details are provided in \textbf{EURO-LABS Deliverable 6.1}. A summary of the measures taken, and those that are ongoing, is presented in the corresponding WP section later in the document. 

The EURO-LABS consortium remains vigilant and committed to maintaining the highest ethical standards across all activities. All ongoing efforts continue to align with the ethics requirements outlined in the project documentation.


\subsection{Explanation of the Work Carried per WP}

This section provides an overview of the work carried out and results achieved per WP. 
during the the \nth{2} \acrshort{RP}.   

\input{sections/WP01}
\input{sections/WP02}
\input{sections/WP03}
\input{sections/WP04}
\input{sections/WP05}
\input{sections/WP06}
% \input{sections/WPxy}

\input{sections/clear_and_measurable_details}

% 1.3 Impact
\input{sections/impact}

% 1.4 
\input{sections/exploitation-dissemination}

% 1.5 Access 
\input{sections/access}

% 1.6 Resources
\input{sections/resources}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%