%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% WP01
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tsubsubsection{WP1 - Project Management and Coordination}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Section content, please change!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Overview and Goals}

\begin{table}[H]
    \renewcommand{\arraystretch}{1.50}		
    \footnotesize   
    \begin{tabular}{*{3}{|p{0.10\textwidth}}|l|}
        \hline
        \rowcolor{mygray} \multicolumn{4}{|c|}{\textit{\color{white}Work Package Summary}} \\
        \hline
        \rowcolor{mylightergray} \textit{WP No.} & \cellcolor{white} 1 & \textit{Title of WP} & \cellcolor{white} Project Management and Coordination (MGT) \\
        \hline
        \rowcolor{mylightergray} \textit{Start} & \cellcolor{white} M1 & \textit{End} & \cellcolor{white} M48 \\
        \hline
        \rowcolor{mylightergray} \multicolumn{4}{|p{0.978\textwidth}|}{\textit{Participating Organisations}} \\
        \hline
        \multicolumn{4}{|p{0.978\textwidth}|}{
            \hspace*{-0.75cm} 
            \begin{minipage}[t]{\textwidth}
    			\begin{itemize}
    			    \item WP Leader: 1-INFN
    				\item Participants: INFN, GANIL, CERN
    			\end{itemize} 
    			\vspace*{0.10em}
			\end{minipage}
        } \\
        \hline
    \end{tabular}
    \vspace{0.5em}\vfill
    \begin{tabular}{|p{0.978\textwidth}|}
        \hline
        \rowcolor{mylightergray} \textit{Goals} \\
        \hline
        \rowcolor{white} 
        \hspace*{-0.75cm} 
        \begin{minipage}[t]{\textwidth}
        \setlength{\parindent}{15pt}
                Task 1.1. Project management and coordination
    		\begin{itemize}
    		    \item Management and steering of the whole project
                    \item Monitoring of the scientific and technical progress in all Work Packages
                    \item Ensuring the contractual and administrative implementation
                    \item Following and reporting on the use of resources
                    \item Preparation of the periodic and final project reports
    		\end{itemize} 
    		\vspace*{0.10em}
	\end{minipage}        
        \\
        \hline
    \end{tabular}
    \vspace{0.5em}\vfill
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{|p{0.25\textwidth}|*{3}{>{\centering\arraybackslash}p{0.252\textwidth}|}}
                    %    {|l|*{3}{>{\centering\arraybackslash}p{0.2\textwidth}|}}
            \hline    
            \rowcolor{mylightergray} \textit{Participant number} & \textit{1} & \textit{2} & \textit{3} \\
            \hline
            \rowcolor{white} \cellcolor{mylightergray}\textit{Participant short name} & INFN & GANIL & CERN \\
            \hline
            \rowcolor{white} \cellcolor{mylightergray}\textit{PM per participant~\footnotemark} & 48 & - & 24 \\
            \hline        
        \end{tabular}
        }
\end{table}
\footnotetext{the PM figures correspond to the full duration of the project.}




\subsubsection*{Status}
The Project Office (PO), coordinated by INFN, is responsible for managing all administrative processes
of EURO-LABS. Together with the Management Team (MT) and the Steering Committee
(SC), the PO ensures the smooth and timely execution of the project and reports to the Governing
Board (GB). The PO also serves as the liaison with the EU Project Officer. There has been no change in the composition of the MT.

\subsubsection*{Progress per Task}

\subparagraph{Task 1:} Project management and coordination \mbox{}

WP1 handled administrative processes and communications with REA and all the beneficiaries.  The PO along with the Steering Committee, ensured a smooth running of the project. Two in-person annual meetings further strengthened the ties between the communities. In the most recent meeting, a new format, having  a large focus on the presentation of selected scientific and technological results conducted  at the various facilities, was adopted. Talks on  the European Strategy of the three communities highlighted the role of EURO-LABS. All the Deliverables and Milestones have been completed in P2 and are available through open access. Various procedures and strategies to facilitate reallocation or balancing of resources, if required, for Transnational Access were finalized by the Governing Board.
The participants were given support for the  implementation of projects, specifically in TNAs and financial aspects, through constant contacts and daily helpdesk via email, telephone and remote
meetings.

\subsubsection*{Main Results and Achievements}
The meetings of the Steering Committee/ Management Team were held on a regular basis, at least bi-monthly. Also periodic management meetings of the Project Office staff were held, in-
volving people from INFN Bologna, INFN Frascati and CERN. Two annual meetings were held in the RP2 period: SAM was organized by IFJ-PAN and held in Krakow, Poland (9th-11th October 2023,
https://agenda.infn.it/event/34651/) and it was attended by 83 participants. TAM was organized by and
held at CERN, Geneva, Switzerland (28th-30th October 2024, https://indico.cern.ch/event/1370378/), with
85 participants. Through a dense agenda of interventions, the three scientific communities have
shared their experiences on TNAs and other activities. During the annual meetings, very appreciated guided tours were also organized to IFJ-PAN and CERN facilities. Two Governing Board
meetings were held during the annual meetings (respectively, 11th Oct. 2023 and 29th Oct. 2024).
They were actively attended. During the 2024 GB meeting, the Chairperson’s mandate was renewed
and the procedure for budget transfers between beneficiaries was approved. These
reports are available on the Funding and Tenders Portal and, when public, on the Zenodo repository
and linked to the project website.


\subsubsection*{Deviations and Corrective Actions}
\label{sec:wp1_deviations}

The amendment did not introduce changes related to WP1 budget items consisting of personnel costs (INFN and CERN).
Considering the total PM provided in the two reporting periods, there are no significant deviations. See table below:

{\fontsize{9}{11}\selectfont
\begin{center}
  \begin{tabular}[t]{!{\color{mygray}\vrule}p{0.10\linewidth}!
  {\color{mygray}\vrule}p{0.10\linewidth}!
  {\color{mygray}\vrule}p{0.10\linewidth}!
  {\color{mygray}\vrule}p{0.10\linewidth}!
  {\color{mygray}\vrule}p{0.10\linewidth}!
 {\color{mygray}\vrule}p{0.10\linewidth}!{\color{mygray}\vrule} } \hline
    \rowcolor{mycyan} & {\bf RP1} & {\bf RP2} & {\bf RP1+RP2} & {\bf Budget} & {\bf Percentage} \\ \hline
    \cellcolor{mycyan}{\bf INFN}: & 14.29 &  24.73 & 39.02 & 48 & 81.29 \% \\ \hline
   \cellcolor{mycyan}{\bf CERN}: & 2.49   &  7.17  & 9.66  & 24 & 40.25 \% \\ \hline 
  \end{tabular}
\end{center}
}

The deviations from what should be the percentage of PM delivered at this point in the project (62.5\%), can be explained by considering the average personnel cost and related offsets.

There were instead budget changes that needed an amendment: those were made for KIT and UMGC, which initially did not contemplate a budget share for the target cost category. More in detail:
\subparagraph{KIT:} Personnel costs were not originally foreseen in the KIT budget because they lost the external manpower supplier (Other goods, works and services) reassigning the EURO-LABS service improvement tasks to a KIT employee (Personnel) and planning to continue to do so in the next reporting periods.
\subparagraph{UMGC:} Considering the activities undertaken within WP2, that include a quarterly basis meeting with the aim of defining needs, strategy and timeline for the implementation of remote-access tools, the need to increase the budget dedicated to "travel and subsistence" was identified.

We profited of the amendment also to introduce some other smaller budget changes that did not imply any substantive or important change to the description of the action in Annex 1 and that would not have formally needed an amendment. These changes can be summarised into three different types:
\subparagraph{Changes 1:} Within WP2, it was deemed appropriate to move the budget share initially dedicated to the cost category "Other goods, works and services" (subcategory "Other"), under the category "Travel and subsistence" (subcategory "User Travel Support ").
This choice was due to the fact that few beneficiaries have made some reevaluations of their consumables from the first version of the budget, underestimating in some cases the reimbursements to the users while overestimating the need for "other goods, works and services" because many of the foreseen purchases were already included in the unit costs.
\subparagraph{Changes 2:} Within WP3, it was deemed necessary to increase the portion of the budget relating to personnel.
\subparagraph{Changes 3:} Within WP4 and partially in WP3, it was decided to request a shift of the relevant budget share from equipment to others cost categories in which there was a necessity. 
This choice was due by some beneficiaries that had not taken into account the fact that the reporting methods relating to Equipment are inefficient. It was decided that a much better approach was to move some of the budget from equipment to other cost categories where there was a necessity.
Moreover in several cases the equipment originally planned in the GA was never specified in detail and it was later realised that this equipment was not absolutely necessary to achieve the tasks and the objectives of the project.


\subsubsection*{Milestones and Deliverables}

{\fontsize{9}{11}\selectfont
\begin{center}
  \begin{tabular}[t]{!{\color{mygray}\vrule}p{0.10\linewidth}!
  {\color{mygray}\vrule}p{0.60\linewidth}!
  {\color{mygray}\vrule}p{0.20\linewidth}!{\color{mygray}\vrule} } \hline
    \rowcolor{mycyan} & {\bf Title} & {\bf Status} \\ \hline
    \cellcolor{mycyan}{\bf D1.1}: & Periodic Report-1 (Sept 2022-Aug 2023) &  Achieved\\ \hline
   \cellcolor{mycyan}{\bf D1.4}: & D27 Policy Brief-2nd release &  Achieved\\ \hline 
  \end{tabular}
\end{center}
}

\subsubsection*{Project Meetings}

\begin{longtable}{|L{0.18\textwidth}|C{0.48\textwidth}|C{0.12\textwidth}|C{0.10\textwidth}|}
\caption{Project meetings during P2}
\label{tab:usp-wp2}
    \\ \hline
    \rowcolor{mycyan}
    {\bf Dates} & {\bf Meeting title and link} &
     {\bf Venue} & {\bf WP} 
    \\ \hline
    \endfirsthead
    \hline
    \rowcolor{mycyan}
        {\bf Dates} & {\bf Meeting title and link} &
     {\bf Venue} & {\bf WP} 
  \\ \hline
    \endhead
    \hline
    \endfoot
    
     12/09/2023 & Management Team \& Steering Committee meeting
https://agenda.infn.it/event/33383/   
  & Zoom & WP1 \\ \hline 
  14/09/2023 & EURO-LABS Project Office meeting (INFN, CERN)
%https://cern.zoom.us/j/67986330971?pwd=QkRNVEJIRkRjWFJyTDBNS2ZPSEtXQT09 
& Zoom & WP1 \\ \hline  
09-11 Oct.2023 & Annual meeting (SAM) and GB meeting
https://agenda.infn.it/event/34651/ & Krakow \& Zoom &  WP1\\ \hline
13/11/2023 & Management Team \& Steering Committee meeting 
https://agenda.infn.it/event/33385/ & Zoom &  WP1\\ \hline
15/11/2023 & EURO-LABS Project Office meeting (INFN, CERN)
%https://infn-it.zoom.us/j/81944998215 
& Zoom & WP1  \\ \hline
08/01/2024 & Management Team \& Steering Committee meeting https://agenda.infn.it/event/33386/ & Zoom & WP1 \\ \hline
10/01/2024 & EURO-LABS Project Office meeting (INFN, CERN)
% https://infn-it.zoom.us/j/81944998215 
& Zoom & WP1 \\ \hline
11/03/2024 & Management Team \& Steering Committee meeting
https://agenda.infn.it/event/39788/ & Zoom & WP1  \\ \hline
22/05/2024 & EURO-LABS Project Office meeting (INFN, CERN) 
% https://cern.zoom.us/j/5750383975?pwd=a3Z0Y3A0MHpVbUx6ZkJKdFhXbUdkZz09 
& Zoom & WP1  \\ \hline
23/05/2024 & Management Team \& Steering Committee meeting 
https://agenda.infn.it/event/39791/ & Zoom & WP1 \\ \hline
16/07/2024 & Management Team \& Steering Committee meeting https://agenda.infn.it/event/39792/ & Zoom & WP1 \\ \hline
16/09/2024 & Management Team \& Steering Committee meeting 
https://agenda.infn.it/event/39793/ & Zoom & WP1  \\ \hline
24/10/2024 & Management Team \& Steering Committee meeting 
https://agenda.infn.it/event/43430/ & Zoom & WP1  \\ \hline
28-30 Oct.2024 & Annual meeting (TAM) and GB meeting
https://indico.cern.ch/event/1370378/ & CERN \& Zoom & WP1  \\ \hline
 %\pagebreak
 %\rowcolor{mycyan}
21/11/2024 & Management Team \& Steering Committee meeting 
https://agenda.infn.it/event/44393/ & Zoom & WP1 \\ \hline 
20/01/2025 & Management Team \& Steering Committee meeting https://agenda.infn.it/event/44716/ & Zoom & WP1 \\ \hline

%\end{tabularx}
\label{tab:wp1-meetings}
\end{longtable}



%  {\color{mygray}\vrule}p{0.40\linewidth}!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%