%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% WP01
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tsubsubsection{WP6 - Ethic Requirements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Section content, please change!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Overview and Goals}

\begin{table}[H]
    \renewcommand{\arraystretch}{1.50}		
    \footnotesize   
    \begin{tabular}{*{3}{|p{0.10\textwidth}}|l|}
        \hline
        \rowcolor{mygray} \multicolumn{4}{|c|}{\textit{\color{white}Work Package Summary}} \\
        \hline
        \rowcolor{mylightergray} \textit{WP No.} & \cellcolor{white} 6 & \textit{Title of WP} & \cellcolor{white} Ethics requirements \\
        \hline
        \rowcolor{mylightergray} \textit{Start} & \cellcolor{white} M1 & \textit{End} & \cellcolor{white} M48 \\
        \hline
        \rowcolor{mylightergray} \multicolumn{4}{|p{0.978\textwidth}|}{\textit{Participating Organisations}} \\
        \hline
        \multicolumn{4}{|p{0.978\textwidth}|}{
            \hspace*{-0.75cm} 
            \begin{minipage}[t]{\textwidth}
    			\begin{itemize}
    			    \item WP Leader : INFN
                        \item Ethics Advisor : Prof. (emeritus) M. Harakeh, Rijksuniversiteit Groningen, Netherlands 
    			\end{itemize} 
    			\vspace*{0.10em}
			\end{minipage}
        } \\
        \hline
    \end{tabular}
    \vspace{0.5em}\vfill
    \begin{tabular}{|p{0.978\textwidth}|}
        \hline
        \rowcolor{mylightergray} \textit{Goals} \\
        \hline
        \rowcolor{white} 
        \hspace*{-0.75cm} 
        \begin{minipage}[t]{\textwidth}
    		\begin{itemize}
    		    \item Setup and ensure compliance with the ethics requirements.
    		\end{itemize} 
    		\vspace*{0.10em}
		\end{minipage}        
        \\
        \hline
    \end{tabular}
    \vspace{0.5em}\vfill
    \resizebox{\textwidth}{!}{%
    \begin{tabular}{|l|>{\centering\arraybackslash}p{0.77\textwidth}|}
        \hline    
        \rowcolor{mylightergray} \textit{Participant number} & \textit{1} \\
        \hline
        \rowcolor{white} \cellcolor{mylightergray}\textit{Participant short name} & INFN \\
        \hline
        \rowcolor{white} \cellcolor{mylightergray}\textit{PM per participant~\footnotemark} & -  \\
        \hline        
    \end{tabular}
    }
\end{table}
\footnotetext{the PM figures correspond to the full duration of the project.}


\subsubsection*{Status}

EURO-LABS aligned with the recommendations described in the report by the  Ethics Advisor.
% confirming that all consortium activities align with the relevant ethics requirements and that no new ethical issues have emerged. Additional details are provided in \textbf{EURO-LABS Deliverable 6.1}. 
 A summary of the measures taken, and those that are ongoing, is presented below. 


The EURO-LABS consortium remains vigilant and committed to maintaining the highest ethical standards across all activities. All ongoing efforts continue to align with the ethics requirements outlined in the project documentation.

\subsubsection*{Progress per Task}

\subparagraph{Health and Safety During Experiments and Training Activities} \mbox{}


EURO-LABS provides Transnational Access (TA) to a wide network of laboratories engaged in cutting-edge research in Accelerator-Based Sciences. These experiments may involve exposure to ionising radiation, posing potential risks to researchers, the public, and the environment. It is worth noting that all EU-based TA facilities comply with EU radiation protection legislation and their respective national laws. Non-EU facilities also adhere to stringent safety regulations. EURO-LABS has implemented and adopted comprehensive procedures to guarantee the health and safety of personnel during all activities.

Mandatory safety training is provided periodically to all employees, and additional procedures are in place for accelerator operations and large installations. Radiation workers receive regular training and testing. Visitors are required to complete safety training and maintain health insurance. All users are equipped with personal dosimeters.

During schools and hands-on training sessions organized by EURO-LABS, the same safety protocols—particularly those concerning ionising radiation, in case of activities implying exposure—are applied to visiting lecturers and students.

\subparagraph{Development of Machine Learning Methods} \mbox{}

Work Package 5.3 involves the development and application of Machine Learning (ML) methods to enhance beam quality, transport efficiency, and reproducibility, thereby reducing the time required for beam tuning.

To ensure ethical compliance, emphasis is placed on transparency, robustness, and avoiding bias in ML methods. Although the techniques could have applications in the medical sector, this is outside the scope of the current project.

The ML development adheres to the \textit{Ethics by Design} and \textit{Ethics of Use} principles, as outlined in the European Commission documents dated 25 November 2021. These principles are followed throughout all phases: design, acquisition, implementation, and monitoring.

The goal of this ML project is to reduce the time required for tuning the beams provided to Transnational Users of EURO-LABS. This will help increase and optimize the time available for research and technological studies, while also reducing power consumption.
The ML applications are restricted to a limited set of machine parameters affecting beam optics and cannot modify arbitrary system settings. Any algorithmic bias could only impact quantifiable properties of the beam (e.g., intensity or size), which are continuously monitored.

The ML algorithms used are fully deterministic and robust against minor external variations. Their application in the project is focused, reliable, transparent, and free of ethical concerns, aimed solely at improving the efficiency of beam tuning for Transnational Users.

% \subsubsection*{Main Results and Achievements}

\subsubsection*{Deviations and Corrective Actions}

None

\subsubsection*{Milestones and Deliverables}

{\fontsize{9}{11}\selectfont
\begin{center}
  \begin{tabular}[t]{!{\color{mygray}\vrule}p{0.10\linewidth}!
  {\color{mygray}\vrule}p{0.60\linewidth}!
  {\color{mygray}\vrule}p{0.20\linewidth}!{\color{mygray}\vrule} } \hline
    \rowcolor{mycyan} & {\bf Title} & {\bf Status} \\ \hline
    \cellcolor{mycyan}{\bf D6.1}: & Ethics - OEI - 24m Update & Achieved \\ \hline
  \end{tabular}
\end{center}
}

\subsubsection*{Project Meetings}

No meetings
%  {\color{mygray}\vrule}p{0.40\linewidth}!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%